### 2018-04-25 Docs/Thesis/docs/chapter5.tex
thesis update

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate all tests using scripts, so our experiments are are fully  reproducible. They are responsible for running all the proposed tests in this chapter and perform the calculations. It includes:

@@

Each test is organized as a Python packege, responsible for tigger all the applications and procedures. The parameters for each simulation can be configured by a \textit{config.py} file. The files \textit{README} on each packege, provide a tutorial to run correctely each test. With all tools instaled, less then fifteen minutes is enought for run each test again. A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.

@@

For each test, we generate a set of plots to compare the original and synthetic trace. Two of them we use for mere visual comparison: flows per second and bandwidth. To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.  On every case, the more closer the plots are, the more similar the traffics are according to each perspective. Also, we wrote in the table ~\ref{tab:results-summary} a complation of each traffic statistics.

@@

For schedule of the timing of traffic generated by each flow, we implemented three methodologies: \texttt{usleep()} C function,\texttt{select()} C function and \textit{pooling}. Here we use \texttt{usleep()} . We implemented the class \texttt{IperfFlow,} responsible for generate the traffic of each flow, using \texttt{popen()} and \texttt{pclose()} to instantiate Iperf processes, responsible for generating the traffic. Traffic customization on Iperf has many limitations. It cannot assign arbitrary IP addresses as source and destination since it must establish a connection between the source and destination. For the transport layer, it just supports TCP and UDP protocol, and constant bandwidth traffic. On the other hand, it enables customization of transmission time, number of packets, windows size, TTL, packet sizes, payload and many other features. Since Iperf has to establish a communication, SIMITAR must operate in the client mode on the source, and server mode on the destinations.

@@

The plot of flows per second seems much more accurate visually since most of the peaks match.  Indeed, no visual lag between the plots. We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot. However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases. It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each stream as fast as possible. So each flow occurrence is restricted to smaller intervals. This behavior can be observed as well in the bandwidth plot. It is much larger in the first seconds and small at the end.

@@

In the first case (figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics. The original skype traffic increased linearly, an indication of fractal shape. The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds). After this scale, the error between the curves become very small. One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds. For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth. For larger scales, it captures the same fractals patterns of the original trace. It also captures a periodicity pattern at the time-scale of 9 seconds. The authors of \cite{swing-paper} measured the same periodicity pattern. But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).

In the second case, on a tree topology on small time scales, the same white-noise behavior is identified. We identify a similar behavior on the energy behavior on larger time-scales, but with a larger gap between the curves. Packet collision on switches requiring retransmission packets explains this behavior. In fact, as we can see in the table ~\ref{tab:results-summary}, two hundred more packets are leaving the client on the tree topology compared to the one-hop.

@@

Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected. It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time. On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.  Some others unexpected behavior must have a more in-depth investigation, such as libtins generating more packets than expected for \textit{skype-pcap}, but not for \textit{lgw10s-pcap}, and why the creation of some flows fail, and how to fix it if possible.

@@

SIMITAR was designed to work at flow-level and packet level. At the flow-level, our methodology can achieve great results. In fact,  The cumulative distribution of flows is almost identical on each case. From the perspective of benchmark of a middle-box such as an SND switch, this is a great result, since its performance depends on the number of registered flows. However, because of packets exchanged by signaling connection, the traffic generated by Iperf, even following the same cumulative flow distribution, had created more streams then expected.

>>>>

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate all tests using scripts, so our experiments are fully reproducible. They are responsible for running all the proposed tests in this chapter and perform the calculations. It includes:

@@

Each test is organized as a Python package, responsible for trigger all the applications and procedures. A \textit{config.py} file can configure the parameters for each simulation. The files \textit{README} on each package, provide a tutorial to run each test correctly. With all tools installed, less then fifteen minutes is enough for rerunning each test. A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specifications and the software versions.

@@

For each test, we generate a set of plots to compare the original and synthetic trace. Two of them we use for visual comparison: flows per second and bandwidth. To examine the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.  In every case, the closer the plots are, the more similar are the traces. Also, we wrote on the table ~\ref{tab:results-summary} a compilation of each traffic statistics.

@@

For schedule of the timing of traffic generated by each flow, we implemented three methodologies: \texttt{usleep()} C function,\texttt{select()} C function and \textit{pooling}. Here we use \texttt{usleep()} . We implemented the class \texttt{IperfFlow,} responsible for generate the traffic of each flow, using \texttt{popen()} and \texttt{pclose()} to instantiate Iperf processes, responsible for generating the traffic. Traffic customization on Iperf has many limitations. It cannot assign arbitrary IP addresses as source and destination since it must establish a connection between the source and destination. For the transport layer, it supports TCP and UDP protocol, and constant bandwidth traffic. On the other hand, it enables customization of transmission time, number of packets, windows size, TTL, packet sizes, payload and many other features. Since Iperf has to establish a communication, SIMITAR must operate in the client mode on the source, and server mode on the destinations.

@@

The plot of flows per second seems much more accurate visually since most of the peaks match.  Indeed, no visual lag between the plots. We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot. However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases. It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each stream as fast as possible. So each flow occurrence is restricted to smaller intervals. This behavior can be observed as well in the bandwidth plot. It is much more significant in the first seconds and small in  the end.

@@

In the first case (figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics. The original skype traffic increased linearly, an indication of fractal shape. The synthetic trace started to grow at the time scale 5-6 (300-600 milliseconds). After this scale, the error between the curves become very small. One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds. For small time scales the traffic become similar to white noise since Iperf emits traffic with constant bandwidth. For larger time-scales, it captures the same fractals patterns of the original trace. It also captures a periodicity pattern at the time-scale of 9 seconds. The authors of \cite{swing-paper} measured the same periodicity pattern. But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).

In the second case, on a tree topology on small time scales, the same white-noise behavior is identified. We identify a similar response for energy on larger time-scales, but with a more significant gap between the curves. Packet collision on switches requiring retransmission packets explains this behavior. In fact, as we can see in the table ~\ref{tab:results-summary}, two hundred more packets are leaving the client on the tree topology compared to the one-hop.

@@

Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected. It is supposed behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time. On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.  Some others unexpected behavior must have a more in-depth investigation, such as libtins generating more packets than expected for \textit{skype-pcap}, but not for \textit{lgw10s-pcap}, and why the creation of some flows fail, and how to fix it if possible.

@@

SIMITAR was designed to work at flow-level and packet level. At the flow-level, our methodology can achieve excellent results. In fact,  The cumulative distribution of flows is almost identical on each case. From the perspective of benchmark of a middle-box such as an SND switch, this is a great result, since its performance depends on the number of registered flows. However, because of packets exchanged by signaling connection, the traffic generated by Iperf, even following the same cumulative flow distribution, had created more streams then expected.

### 2018-04-25 Docs/Thesis/docs/chapter6.tex
update
thesis update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion and Future Work}\label{ch:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. If it is smaller, SIMITAR just uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is poor. Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve a more reasonable performance for individual flows, and reduce the processing time.

(5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}. DPDK KNI interfaces allow applications from the user's space interact with DPDK ports. In this way, we may achieve a faster packet processing. This can be integrated as an insatiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).

@@

(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be splitted on $m$ different files, each describing $n/m$ flows, and still describe the same traffic. With $m$ synchronized machines woking in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-agregattion techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.

(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation. Modelling inter-packet times the scaling characteristics of libtins traffic should improve.

@@

(15) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance. Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads. This action should not impact on throughput and scaling characteristics because few packets would be ignored. But it can increase the precision of the most significant flows since all the threads are competing for each other on the Operational System. But, the number of flows created would be smaller.

(16) Currently, SIMITAR only enables the programming of flow traffic generation in C++. Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.

@@

%Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.  We can create not just Simitar trace descriptors, but Swing and Harpoon trace descriptors as well. So, as here, we would have the same components: the Sniffer, the SQLite database, the DataProcessor, the flow generator, and the same interface based on an XML Compact Trace Descriptor. The FlowGenerator would abstract the traffic generation in based on the Swing and Harpoon model, in an API independent way as well.

%These implementations can lead to a definitive and standardized model of realistic traffic generation. In this way, progresses on high-speed traffic generation would no more make old traffic generators and models obsolete. Also, would enable the comparison (ain a fair way) which model is actually the best since the same engine and technic for generating packets will be used.

%Also, the idea of a Compact Trace Descriptor, by itself separates the idea of traffic generation and the modeling. De development of new methodologies for modeling is  separated from the traffic generation. So a data-developer, using any compact trace descriptor interface may just "plug" his method of data modeling in the FlowGenerator. He has not to care about how the packets were going to be generated anymore nor in what programming language is being used to craft packets.

@@

In this dissertation we discuss our process of conceiving, researching, definition and development and validation of an realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available proposals. This was not a linear procedure. Was indeed an espiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}. Clealy its not identical, because we adapt it for research purposes. At the figure~\ref{fig:spiral} we show a diagram of who  it was done.

@@

We started defining our goals creating a task list, formalizing it on "Working Plan" documents. These tasks lists covered the whole process and included research, the study of new subjects, implementation, and testing. Next, search on the literature the state of things, related works and points for innovation. At this point, we defined the concepts of our traffic generator. We create an architecture model using UML, defining the software components, classes and sequence diagrams. This initial step was crucial since, in later stages, changes in the architecture design are much more difficult. In fact, some small changes such as directory structure and new classes are inevitable. But structural changes are impracticable. At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.

@@

In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution of our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times. Both can infer a good model, even evaluated according to different types of metrics, without any simulation. Also, we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference. As far as is our knowledge, this is a complete study on the use of AIC and BIC on inter-packet times modeling of Ethernet traffic.

In the end, we were able to implement a functional implementation of the solution proposed in the chapter ~\ref{ch:introduction}. Our main contribution here is the development of a traffic generator tool that at the same time can provide realistic synthetic traffic, and its modeling framework is extensible for most of the traffic generation libraries and tools. In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.

@@

Finally, we created a list of improvements and future works, aiming the improvement of the software, inclusing, performance better processing time and packet generation, and the realismo on the traffic generated. In fact, the greater bootleneck of the project resides on processing performance. The results on realism, even with a lot of room for improovments, already have a good quality. With the proposed future works we believe to be possible overcome the current limitations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Future Work and Final Conclusions}\label{ch:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount. Otherwise, SIMITAR uses the constant model. We decide to do it for two reasons. First, because with a small sample, the modeling accuracy is reduced. Second, we avoid the cost of the parameterization process. Now, its value is set to Its value today is set to 30. Increasing this amount, we may achieve more reasonable performance for individual flows, and reduce the processing time.

(5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}. DPDK KNI interfaces allow applications from the user's space interact with DPDK ports. In this way, we may achieve a faster packet processing. This can be integrated as an instantiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).

@@

(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic. With $m$ synchronized machines working in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-aggregation techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.

(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads,  the values of inter-packet times must be calculated before the actual traffic generation. Modeling inter-packet times the scaling characteristics of libtins traffic should improve.

@@

(15) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance. Since SIMITAR manages each flow in a different thread, it will generate fewer threads simultaneously, reducing overheads. This action should not impact on throughput and scaling characteristics because few packets would be ignored. But it can increase the precision of the most significant flows since all the threads are competing for each other on the Operational System. But, the number of flows created would be smaller.

(16) Currently, SIMITAR only enables the programming of flow traffic generation in C++. Adding Python and Lua support for the Flow Generator component, we can allow expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.

@@

%Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.  We can create not just SIMITAR trace descriptors, but Swing and Harpoon trace descriptors as well. So, as here, we would have the same components: the Sniffer, the SQLite database, the DataProcessor, the flow generator, and the same interface based on an XML Compact Trace Descriptor. The FlowGenerator would abstract the traffic generation based on the Swing and Harpoon model, in an API independent way as well.

%These implementations can lead to a definitive and standardized model of realistic traffic generation. In this way, progresses on high-speed traffic generation would no more make old traffic generators and models obsolete. Also, would enable the comparison (in a fair way) which model is the best since the same engine and technic for generating packets will be used.

%Also, the idea of a Compact Trace Descriptor, by itself separates the concept of traffic generation and the modeling. The development of new methodologies for modeling is divided from the traffic generation. So a data-developer, using any small trace descriptor interface may just "plug" his method of data modeling in the FlowGenerator. He has not to care about how the packets were going to be generated anymore nor in what programming language is being used to craft packets.

@@

In this dissertation, we discuss our process of conceiving, researching, definition and development and validation of a realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available suggestions. This was not a linear procedure. Was indeed a spiral procedure, as proposed by Sommerville on Software Engineering\cite{sommerville}. It's not identical, because we adapt it for research purposes. At the figure~\ref{fig:spiral} we show a diagram of how we do it.

@@

We started defining our goals creating a task list, formalizing it on "Working Plan" documents. These tasks lists covered the whole process and included research, the study of new subjects, implementation, and testing. Next, search on the literature the state of things, related works and points for innovation. At this point, we defined the concepts of our traffic generator. We create an architecture model using UML, defining the software components, classes and sequence diagrams. This initial step was crucial since, in later stages, changes in the architecture design are much more difficult. In fact, some small changes such as directory structure and new classes are inevitable. But structural changes are impracticable. At this point we implemented a simple prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.

@@

In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution to our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times. Both can infer a good model, even evaluated according to different types of metrics, without any simulation. Also, we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference. As far as is our knowledge, this is a complete study on the use of AIC and BIC on inter-packet times modeling of Ethernet traffic.

In the end, we were able to implement a functional implementation of the solution proposed in the chapter ~\ref{ch:introduction}. Our main contribution here is the development of a traffic generator tool that at the same time can provide realistic synthetic traffic, and its modeling framework is extensible for most of the traffic generation libraries and tools. In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the application of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.

@@

Finally, we created a list of improvements and future works, aiming the development of the software, including, performance better processing time and packet generation, and the realism on the traffic generated. In fact, the higher bottleneck of the project resides on processing performance. The results on realism, even with a lot of room for improvement, already have a good quality. With the proposed future works we believe to be possible overcome the current limitations.

### 2018-04-25 Docs/Thesis/docs/macros.tex
updates
up
thesis update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Year}{
	Anderson dos Santos Paschoalon
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TituloDaTese}{
SIMITAR: Uma Ferramente para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes
}

@@

Gostaria de agradecer ao meu professor e orientador Christian Esteves Rothemberg, sem o qual, seja pelo ensino, seja pela orientação e apoio durante o projeto, este trabalho não teria saído do papel.

@@

E por ultimo agradeço a Deus por todos seu dons, proteção aamor

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Year}{
	2017
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TituloDaTese}{
SIMITAR: Uma Ferramenta para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes
}

@@

Gostaria de agradecer ao meu professor e orientador Christian Esteves Rothemberg, sem o qual, seja pelo ensino, seja pela orientação e apoio durante o projeto, este trabalho não teria saído do papel. Gostaria de agredecer toda sua paciencia e entendimento por esses ultimos anos.Sua liderança será uma fonte de inspiração para mim para o restante de minha carreira, e ela está apenas começando. Sem sua idéias  inovadoras, suporte e encorajamento continuo, este projeto não teria saido do papel. Especialmente pelo fato de que em pesquisa muitas vezes as coisas não saem como o esperado, e temos que reiniciar do zero o processo.

@@

E por ultimo agradeço a Deus por todos seu dons, proteção e amor.
